HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-10 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

The M4 competition proposes 3 metrics to evaluate the different approaches: the mean absolute scaled error (MASE), the symmetric mean absolute percentage error (SMAPE) and the overall weighted average (OWA). MASE and SMAPE are defined as follow:
\begin{align*}
&\mathrm{MASE} = \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,
&\mathrm{SMAPE} = \frac{2}{h}\sum_{j=1}^h\frac{|Y_{T+j} - \hat{Y}_{T+j}|}{|Y_{T+j}| + |\hat{Y}_{T+j}|}\,,
\end{align*}
where h is the forecast horizon and m the length of the seasonality. The final OWA is computed by following these steps: i) compute the average MASE and SMAPE of a model. ii) Divide the previous results by the MASE and SMAPE computed with the benchmark method \textit{snaïve}. iii) Compute the OWA as the average of the relative MASE and SMAPE obtained is step ii). As an example on the m4 weekly dataset, the method \textit{hermes-tbats} gets a MASE of 7.383 and a SMAPE of 2.191. The benchmark method \textit{snaïve} obtains a MASE of 9.161 and a SMAPE of 2.777. Thus the OWA of  \textit{hermes-tbats} is equal to 0.797.
\begin{equation*}
    OWA_{\textit{hermes-tbats}} = \frac{1}{2}(\frac{7.282}{9.161} + \frac{2.191}{2.777}) \approx 0.797
\end{equation*}

>>>>

The M4 competition proposes 3 metrics to evaluate the different approaches: the mean absolute scaled error (MASE), the symmetric mean absolute percentage error (SMAPE) and the overall weighted average (OWA). MASE and SMAPE are defined as follow:
\begin{align*}
&\mathrm{MASE} = \frac{T-m}{h}\frac{\sum_{j=1}^h |Y_{T+j} - \hat{Y}_{T+j}| }{\sum_{i=1}^{T-m} |Y_i - Y_{i-m}|}\,,
&\mathrm{SMAPE} = \frac{2}{h}\sum_{j=1}^h\frac{|Y_{T+j} - \hat{Y}_{T+j}|}{|Y_{T+j}| + |\hat{Y}_{T+j}|}\,,
\end{align*}
where h is the forecast horizon and m the length of the seasonality. The final OWA is computed by following these steps: i) compute the average MASE and SMAPE of a model. ii) Divide the previous results by the MASE and SMAPE computed with the benchmark method \textit{snaïve}. iii) Compute the OWA as the average of the relative MASE and SMAPE obtained is step ii). As an example on the M4 weekly dataset, the method \textit{hermes-tbats} has a MASE of 7.383 and a SMAPE of 2.191. The benchmark method \textit{snaïve} has a MASE of 9.161 and a SMAPE of 2.777. Thus the OWA of  \textit{hermes-tbats} is equal to 0.797.
%\begin{equation*}
%    OWA_{\textit{hermes-tbats}} = \frac{1}{2}(\frac{7.282}{9.161} + \frac{2.191}{2.777}) \approx 0.797
%\end{equation*}
